IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-07 paper/extensions.tex
clearance fix

\paragraph{Clearance}
%
LIO, SWAPI, and Breeze additionally provide a discretionary access
control mechanism---called \emph{clearance}---at the language
level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
This mechanisms is
used to restrict a computation from accessing data (or communicating
with entities) above a specified label, the clearance.
%
For simplicity, we omitted clearance from our formalism.
%
We only remark that the mechanism generalizes beyond these IFC systems
in a straight forward manner and does not affect our definitions or
proofs in any meaningful way.

>>>>

\paragraph{Clearance}
%
LIO, SWAPI, and Breeze additionally provide a discretionary access
control (DAC) mechanism---called \emph{clearance}---at the language
level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
%
This mechanisms is used to restrict a computation from allocating and
accessing data (or communicating with entities) above a specified
label, the clearance.
%
Amending our IFC language with clearance is mostly straight forward,
and, in particular, does not not affect our definitions or proofs in
any meaningful way.
%
To this end, we first extend tasks to track a clearance label
alongside the current label, and amend the core IFC language with two
new terminals for retrieving and setting this value (see
Appendix~\ref{sec:appendix-extensions}).
%
Since this extension simply adds a per-task global mutable variable,
our security guarantees hold trivially.
%
Of course this also does not provide any notion of DAC.
%
To do so we restrict the language with $\mathcal{P}_\text{clearance}$,
the family of always valid predicates, except for the ones for
rules that raise the current label (e.g., \textsc{I-setLabel}) or
perform allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}).
%
The predicate for \textsc{I-setLabel} is: $P = |il canFlowTo il'|$,
where |il'| is the clearance and |il| is the current label.
%
As further discussed in Appendix~\ref{sec:appendix-extensions},
similar predicates are used in some of the rules of the calculus
extended with labeled values and references.
